DSCI 445 - Utilizing Machine Learning for Algae Predictions

### 2020-12-11 slides.Rmd
Update slides.Rmd
fix image paths
Added suggested changes.

![](map.jpeg)

@@

![](HT_Monthly.jpeg)

@@

![](HT_Obs.jpeg)

@@

![](ht_color_dist.jpeg)

@@

![](HT_Climatology.jpeg)

@@

![](ht_color_over_time.jpeg)

## Methodology

@@

@@

@@

- We can interpret residuals as the **negative gradient** of the total loss
  defined before.
- Update $F(\cdot)$ based on the negative gradient of our total loss.
- This algorithm can handle different loss functions, with different
  properties, making it very flexible.
- Here, we use the default implementation in `scikit-learn`, which has a
  least-squares loss function:

>>>>

![](images/map.jpeg)

@@

![](images/HT_Monthly.jpeg)

@@

![](images/HT_Obs.jpeg)

@@

![](images/ht_color_dist.jpeg)

@@

![](images/HT_Climatology.jpeg)

@@

![](images/ht_color_over_time.jpeg)

## Merge Threshold

- In-situ and satellite data do not necessarily have matching dates
- On an inner join, most of the data would be dropped
- Solution: Shift in-situ data $0, \cdots, n$ days forward and backward

## Response Variable Transformation

Because of extreme skew, the response variable, chlorophyll, was
log-transformed.

@@

## Model selection

- Final model was selected via 5-fold cross-validation error on a training set.
- Models were fit over a grid of:
  1. Model type
  1. Variable Subset
  1. Merge Threshold

@@

![](images/gradient_boosting_simple.png)

Image credit: https://arogozhnikov.github.io/2016/06/24/gradient_boosting_explained.html

@@

- We can interpret residuals as the **negative gradient** of the total loss.
- Here, we use the default implementation in `scikit-learn`, which has a
  least-squares loss function:
